---
title: "Exploratory Data Analysis"
author: "Luis Talavera"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(sentimentr) 
library(R.utils)
library(wordcloud)
library(RColorBrewer)
library(hunspell)
```

## Goal of analysis

The main goal is of this analysis is explore the corpus to identify key aspects of data, how many words each file have, how many lines each file have, how many words represent a certain percentage of the text.

For this analysis, we will explore US blogs, tweets and news, plot words frequency and analyze the most common 2-grams and 3-grams (combinations of 2 or 3 words).


## Get data

First we download the data from URL.

```{r get_data, echo=FALSE}
zip_url <- "https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip"
zip_file <- "Coursera-Swiftkey.zip"
data_dir <- "./data/final"
lang_dir <- "/en_US/"
file_name <- list(blogs = "en_US.blogs.txt",
                  news = "en_US.news.txt",
                  twitter = "en_US.twitter.txt")
file_paths <- lapply(file_name, function(name) { paste0(data_dir,lang_dir, name) })


if(!file.exists(paste0("./data/", zip_file))) {
  download(zip_url)
}

if(!file.exists(data_dir)) {
  setwd("./data")
  unzip(zip_file)
  setwd("../")
}

```

Now we will show basic summaries: file lines, words, word frequency
```{r summary, cache=TRUE}
file_lines <- sapply(file_name, function(x) {
  as.numeric(countLines(paste0(data_dir, lang_dir, x)))
  })

tibble(File = unlist(file_name), Lines = file_lines)
```

We are going to subset data to continue exploring data.
```{r subset_data}

sample_text <- function(file_name, output_name) {
  set.seed(1234)
  
  lines <- read_lines(file_name)
  
  n_lines <- as.numeric(countLines(file_name))
  
  size <- ifelse(n_lines/1000 > 1000, n_lines/1000, 1000)
  
  selected_lines <- sample(n_lines, size = size, replace = FALSE)
  subset_text <- lines[selected_lines]
  
  write_lines(subset_text, output_name)
}


sample_name <- lapply(file_name, function(name) { paste0("sample_", name) })
sample_paths <- lapply(sample_name, function(name) { paste0(data_dir,lang_dir, name) })

# Sample Blogs data
if(!file.exists(paste0(data_dir,lang_dir,sample_name["blogs"]))) {
  sample_text(paste0(data_dir,lang_dir,file_name["blogs"]),
              paste0(data_dir,lang_dir,sample_name["blogs"]))
}

# Sample News data
if(!file.exists(paste0(data_dir,lang_dir,sample_name["news"]))) {
  sample_text(paste0(data_dir,lang_dir,file_name["news"]),
              paste0(data_dir,lang_dir,sample_name["news"]))
}

# Sample Twitter data
if(!file.exists(paste0(data_dir,lang_dir,sample_name["twitter"]))) {
  sample_text(paste0(data_dir,lang_dir,file_name["twitter"]),
              paste0(data_dir,lang_dir,sample_name["twitter"]))
}
```
### Blog data

First 10 lines of blog data sample

```{r blog_read}
blog_lines <- read_lines(sample_paths["blogs"])
head(blog_lines, 10)
```

```{r blog_data_structure}
# Create a list to store all data transformations
blog_data <- list()
```


To analyze words is necessary to split each line into tokens, this process is called tokenization.

```{r blog_token}
blog_data$text_tibble <- tibble(line = 1:length(blog_lines), text = blog_lines)
blog_data$original <- blog_data$text_tibble %>% 
                 unnest_tokens(token, text, strip_punct = TRUE) %>%
                 filter(!is.na(token)) %>%
                 mutate(word = token)

# Remove stopwords
blog_data$wo_stepwords <- blog_data$original %>%
                     anti_join(stop_words, by=c("token"="word"))
```



```{r blog_profanity_filtering, warning=FALSE}
# Using sentimentr
blog_data$sentences <- get_sentences(blog_lines)

profanity_terms <- extract_profanity_terms(blog_data$sentences) # names: neutral, profanity, sentence

profane_words <- unique(unlist(profanity_terms$profanity))

# Filter profanity
blog_data$wo_profanity <- blog_data$wo_stepwords %>%
                     filter(!token %in% profane_words)
```


```{r blog_data_cleaning}
# Remove numbers
blog_data$wo_numbers <- blog_data$wo_profanity %>% filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word))

# Remove misspelled words
blog_data$correct_words <- blog_data$wo_numbers %>% filter(hunspell_check(word))
```

### 1-gram
```{r blog_word frequency, echo=FALSE}
wf <- count(blog_data$correct_words, word, sort = TRUE)
wf10 <- head(wf,15)

ggplot(wf10, aes(x=reorder(word, n), y=n, fill = word)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Word")
```

```{r blog_wordcloud, echo=FALSE}
set.seed(1234)
wordcloud(words = wf$word, freq = wf$n, min.freq = 10,
          max.words=100, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r blog_bing, echo=FALSE}
blog_data$bing_word_counts <- blog_data$wo_profanity %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()



blog_data$bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


```{r blog_nrc, echo=FALSE}
blog_data$nrc_word_counts <- blog_data$wo_profanity %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

blog_data$nrc_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


### 2-gram
```{r blog_2gram}
blog_data$bigram <- blog_data$text_tibble %>% 
                 unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
                 filter(!is.na(bigram))
```

2-grams with stop words.

```{r blog_bigram_clean}
bigrams_separated <- blog_data$bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2))

blog_data$bigrams_separated <- bigrams_filtered
blog_data$bigrams_filtered <- bigrams_filtered %>%
                         unite(bigram, word1, word2, sep = " ")
```

```{r blog_barlpot_bigram, echo=FALSE}
bf <- count(blog_data$bigrams_filtered, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

2-grams without stop words.

```{r blog_bigram_clean_stopwords}
blog_data$bigrams_wo_stepwords <- blog_data$bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  unite(bigram, word1, word2, sep = " ")
```

```{r blog_barlpot_bigram_stopwords, echo=FALSE}
bf <- count(blog_data$bigrams_wo_stepwords, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

### 3-gram

3-gram with stop words

```{r blog_3gram}
blog_data$trigram <- blog_data$text_tibble %>% 
                 unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
                 filter(!is.na(trigram))
```

```{r blog_trigram_clean}
trigrams_separated <- blog_data$trigram %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ")

trigrams_filtered <- trigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!word3 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!is.na(word3)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word3)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2)) %>%
  filter(hunspell_check(word3))

blog_data$trigrams_separated <- trigrams_filtered
blog_data$trigrams_filtered <- trigrams_filtered %>%
                         unite(trigram, word1, word2, word3, sep = " ")
```

```{r blog_barlpot_trigram, echo=FALSE}
tf <- count(blog_data$trigrams_filtered, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```

3-gram without stop words

```{r blog_trigram_clean_stopwords}
blog_data$trigrams_wo_stopwords <- blog_data$trigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word3 %in% stop_words$word) %>%
  unite(trigram, word1, word2, word3, sep = " ")
```

```{r blog_barlpot_trigram_stopwords, echo=FALSE}
tf <- count(blog_data$trigrams_wo_stopwords, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```

### News data

First 10 lines of news data sample

```{r news_read}
news_lines <- read_lines(sample_paths["news"])
head(news_lines, 10)
```

```{r news_data_structure}
# Create a list to store all data transformations
news_data <- list()
```


Tokenize news data to later perform a word analysis.

```{r news_token}
news_data$text_tibble <- tibble(line = 1:length(news_lines), text = news_lines)
news_data$original <- news_data$text_tibble %>% 
                 unnest_tokens(token, text, strip_punct = TRUE) %>%
                 filter(!is.na(token)) %>%
                 mutate(word = token)

# Remove stopwords
news_data$wo_stepwords <- news_data$original %>%
                     anti_join(stop_words, by=c("token"="word"))
```



```{r news_profanity_filtering, warning=FALSE}
# Using sentimentr
news_data$sentences <- get_sentences(news_lines)

profanity_terms <- extract_profanity_terms(news_data$sentences) # names: neutral, profanity, sentence

profane_words <- unique(unlist(profanity_terms$profanity))

# Filter profanity
news_data$wo_profanity <- news_data$wo_stepwords %>%
                     filter(!token %in% profane_words)
```


```{r news_data_cleaning}
# Remove numbers
news_data$wo_numbers <- news_data$wo_profanity %>% filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word))

# Remove misspelled words
news_data$correct_words <- news_data$wo_numbers %>% filter(hunspell_check(word))
```

### 1-gram
```{r news_word frequency, echo=FALSE}
wf <- count(news_data$correct_words, word, sort = TRUE)
wf10 <- head(wf,15)

ggplot(wf10, aes(x=reorder(word, n), y=n, fill = word)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Word")
```

```{r news_wordcloud, echo=FALSE, warning=FALSE}
set.seed(1234)
wordcloud(words = wf$word, freq = wf$n, min.freq = 10,
          max.words=100, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r news_bing, echo=FALSE}
news_data$bing_word_counts <- news_data$wo_profanity %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()



news_data$bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


```{r news_nrc, echo=FALSE}
news_data$nrc_word_counts <- news_data$wo_profanity %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

news_data$nrc_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


### 2-gram
```{r news_2gram}
news_data$bigram <- news_data$text_tibble %>% 
                 unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
                 filter(!is.na(bigram))
```

2-grams with stop words.

```{r news_bigram_clean}
bigrams_separated <- news_data$bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2))

news_data$bigrams_separated <- bigrams_filtered
news_data$bigrams_filtered <- bigrams_filtered %>%
                         unite(bigram, word1, word2, sep = " ")
```

```{r news_barlpot_bigram, echo=FALSE}
bf <- count(news_data$bigrams_filtered, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

2-grams without stop words.

```{r news_bigram_clean_stopwords}
news_data$bigrams_wo_stepwords <- news_data$bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  unite(bigram, word1, word2, sep = " ")
```

```{r news_barlpot_bigram_stopwords, echo=FALSE}
bf <- count(news_data$bigrams_wo_stepwords, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

### 3-gram

3-gram with stop words

```{r news_3gram}
news_data$trigram <- news_data$text_tibble %>% 
                 unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
                 filter(!is.na(trigram))
```

```{r news_trigram_clean}
trigrams_separated <- news_data$trigram %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ")

trigrams_filtered <- trigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!word3 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!is.na(word3)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word3)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2)) %>%
  filter(hunspell_check(word3))

news_data$trigrams_separated <- trigrams_filtered
news_data$trigrams_filtered <- trigrams_filtered %>%
                         unite(trigram, word1, word2, word3, sep = " ")
```

```{r news_barlpot_trigram, echo=FALSE}
tf <- count(news_data$trigrams_filtered, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```

3-gram without stop words

```{r news_trigram_clean_stopwords}
news_data$trigrams_wo_stopwords <- news_data$trigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word3 %in% stop_words$word) %>%
  unite(trigram, word1, word2, word3, sep = " ")
```

```{r news_barlpot_trigram_stopwords, echo=FALSE}
tf <- count(news_data$trigrams_wo_stopwords, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```


### Twitter data

First 10 lines of twitter data sample

```{r twitter_read}
twitter_lines <- read_lines(sample_paths["twitter"])
head(twitter_lines, 10)
```

```{r twitter_data_structure}
# Create a list to store all data transformations
twitter_data <- list()
```


Tokenize twitter data to later perform a word analysis.

```{r twitter_token}
twitter_data$text_tibble <- tibble(line = 1:length(twitter_lines), text = twitter_lines)
twitter_data$original <- twitter_data$text_tibble %>% 
                 unnest_tokens(token, text, strip_punct = TRUE) %>%
                 filter(!is.na(token)) %>%
                 mutate(word = token)

# Remove stopwords
twitter_data$wo_stepwords <- twitter_data$original %>%
                     anti_join(stop_words, by=c("token"="word"))
```



```{r twitter_profanity_filtering, warning=FALSE}
# Using sentimentr
twitter_data$sentences <- get_sentences(twitter_lines)

profanity_terms <- extract_profanity_terms(twitter_data$sentences) # names: neutral, profanity, sentence

profane_words <- unique(unlist(profanity_terms$profanity))

# Filter profanity
twitter_data$wo_profanity <- twitter_data$wo_stepwords %>%
                     filter(!token %in% profane_words)
```


```{r twitter_data_cleaning}
# Remove numbers
twitter_data$wo_numbers <- twitter_data$wo_profanity %>% filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word))

# Remove misspelled words
twitter_data$correct_words <- twitter_data$wo_numbers %>% filter(hunspell_check(word))
```

### 1-gram
```{r twitter_word frequency, echo=FALSE}
wf <- count(twitter_data$correct_words, word, sort = TRUE)
wf10 <- head(wf,15)

ggplot(wf10, aes(x=reorder(word, n), y=n, fill = word)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Word")
```

```{r twitter_wordcloud, echo=FALSE, warning=FALSE}
set.seed(1234)
wordcloud(words = wf$word, freq = wf$n, min.freq = 10,
          max.words=100, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r twitter_bing, echo=FALSE}
twitter_data$bing_word_counts <- twitter_data$wo_profanity %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()



twitter_data$bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


```{r twitter_nrc, echo=FALSE}
twitter_data$nrc_word_counts <- twitter_data$wo_profanity %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

twitter_data$nrc_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


### 2-gram
```{r twitter_2gram}
twitter_data$bigram <- twitter_data$text_tibble %>% 
                 unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
                 filter(!is.na(bigram))
```

2-grams with stop words.

```{r twitter_bigram_clean}
bigrams_separated <- twitter_data$bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2))

twitter_data$bigrams_separated <- bigrams_filtered
twitter_data$bigrams_filtered <- bigrams_filtered %>%
                         unite(bigram, word1, word2, sep = " ")
```

```{r twitter_barlpot_bigram, echo=FALSE}
bf <- count(twitter_data$bigrams_filtered, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

2-grams without stop words.

```{r twitter_bigram_clean_stopwords}
twitter_data$bigrams_wo_stepwords <- twitter_data$bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  unite(bigram, word1, word2, sep = " ")
```

```{r twitter_barlpot_bigram_stopwords, echo=FALSE}
bf <- count(twitter_data$bigrams_wo_stepwords, bigram, sort = TRUE)
bf10 <- head(bf,20)

ggplot(bf10, aes(x=reorder(bigram, n), y=n, fill = bigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Bigram")
```

### 3-gram

3-gram with stop words

```{r twitter_3gram}
twitter_data$trigram <- twitter_data$text_tibble %>% 
                 unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
                 filter(!is.na(trigram))
```

```{r twitter_trigram_clean}
trigrams_separated <- twitter_data$trigram %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ")

trigrams_filtered <- trigrams_separated %>%
  filter(!word1 %in% profane_words) %>%
  filter(!word2 %in% profane_words) %>%
  filter(!word3 %in% profane_words) %>%
  filter(!is.na(word1)) %>%
  filter(!is.na(word2)) %>%
  filter(!is.na(word3)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word1)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word2)) %>%
  filter(!grepl("^(\\d+(,\\d+)*(.\\d+))|(\\d+)$", word3)) %>%
  filter(hunspell_check(word1)) %>%
  filter(hunspell_check(word2)) %>%
  filter(hunspell_check(word3))

twitter_data$trigrams_separated <- trigrams_filtered
twitter_data$trigrams_filtered <- trigrams_filtered %>%
                         unite(trigram, word1, word2, word3, sep = " ")
```

```{r twitter_barlpot_trigram, echo=FALSE}
tf <- count(twitter_data$trigrams_filtered, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```

3-gram without stop words

```{r twitter_trigram_clean_stopwords}
twitter_data$trigrams_wo_stopwords <- twitter_data$trigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word3 %in% stop_words$word) %>%
  unite(trigram, word1, word2, word3, sep = " ")
```

```{r twitter_barlpot_trigram_stopwords, echo=FALSE}
tf <- count(twitter_data$trigrams_wo_stopwords, trigram, sort = TRUE)
tf10 <- head(tf,20)

ggplot(tf10, aes(x=reorder(trigram, n), y=n, fill = trigram)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  coord_flip() +
  xlab("Trigram")
```


==================================================================================
## Questions to consider

Some words are more frequent than others - what are the distributions of word frequencies? 

What are the frequencies of 2-grams and 3-grams in the dataset? 

How many unique words do you need in a frequency sorted dictionary to cover 50% of all word instances in the language? 90%? 

How do you evaluate how many of the words come from foreign languages? 

Can you think of a way to increase the coverage -- identifying words that may not be in the corpora or using a smaller number of words in the dictionary to cover the same number of phrases?



==========================================================
TODO: 
Contar palabras y palabras únicas de las muestras